### 2018-03-17 paper/6-engineering.tex
Add a relaxed correctness definition for shallow builds

\begin{description}
\item[Materialisation] Sometimes input files will involve many intermediate tasks
before producing the end result, e.g. an installer package. These intermediate
steps may be large, so some cloud builds can execute the graph \emph{without}
downloading or \emph{materialising} the results of intermediate tasks -- only
the final result. Some build systems can go even further, integrating with the
file system to only materialise the file when the user accesses it \cite{gvfs}.

\item[Eviction] The store of traces as shown grows indefinitely, but often
resource constraints require evicting old items from the store. One option is
to evict the contents and any trace that mentions the now-defunct
\hs{Hash}~\hs{v}. However, if the build system can defer materialisation, it
may be possible to only evict the contents, allowing builds to pass-through
hashes of values where the underlying value is not known. If so, the build must
be able to recreate the value if required, potentially dealing with a different
result in a future run.

@@

\item[Offloading] Once the cloud is storing build products and traces, it is
possible for the cloud to also contain dedicated workers that can execute tasks
remotely~--~offloading some of the computation and potentially running vastly
more commands in parallel.
\end{description}

>>>>

\begin{description}
\item[Eviction] The store of traces as shown grows indefinitely, but often
resource constraints require evicting old items from the store. One option is
to evict the contents and any trace that mentions the now-defunct
\hs{Hash}~\hs{v}. However, if the build system can defer materialisation, it
may be possible to only evict the contents, allowing builds to pass-through
hashes of values where the underlying value is not known. If so, the build must
be able to recreate the value if required, potentially dealing with a different
result in a future run.

@@

\item[Offloading] Once the cloud is storing build products and traces, it is
possible for the cloud to also contain dedicated workers that can execute tasks
remotely~--~offloading some of the computation and potentially running vastly
more commands in parallel.

\item[Shallow builds] Sometimes input files will involve many intermediate tasks
before producing the end result, e.g. an installer package. These intermediate
steps may be large, so some cloud build systems are designed to build end
products \emph{without} downloading or \emph{materialising} the results of
intermediate tasks~--~only the final result~--~a so-called \emph{shallow build}.
Some build systems can go even further, integrating with the file system to only
materialise the file when the user accesses it \cite{gvfs}.
\end{description}

To legitimise shallow builds, we need to relax the correctness
Definition~\ref{def-correct} as follows. Let the \hs{shallow} store correspond
to the result of a shallow build. Then \hs{shallow} is correct, if \emph{there
exists} \hs{result} which satisfies all requirements of
Definition~\ref{def-correct}, \emph{such that} \hs{shallow} agrees with
\hs{result} on the input keys \hs{k}~$\in$~$I$:
\[
\hs{getValue}~\hs{k}~\hs{shallow}~\hs{==}~\hs{getValue}~\hs{k}~\hs{result}
\]
and on the target \hs{key}:
\[
\hs{getValue}~\hs{key}~\hs{shallow}~\hs{==}~\hs{getValue}~\hs{key}~\hs{result}.
\]

\noindent
This relaxes the requirements on shallow builds by dropping the constraints on
the \hs{shallow} store for all intermediate keys \hs{k}~$\in$~$O\setminus \{\hs{key}\}$.
